\documentclass{article}
\usepackage{nips12submit_e,times}

\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{graphicx, subfigure, fink, grffile, placeins}
\usepackage{hyperref}
\usepackage{color}
\usepackage{url}
\usepackage{algorithm}
\usepackage{algpseudocode}
\usepackage{upgreek}

% \title{Modeling Network and Text Structure in Online Forums}
% \title{Simultaneous text \& Network modeling in MMSB for Learning Structured
% Interactions on Online Forums}
% \title{Modeling Structured Interaction in Big Online User Forums }
% \title{Modeling Structured Interaction in \\ Large Online User Forums }
\title{A probabilistic approach for modeling user interactions in thread-based 
online discussion forums}

% \author{
% Abhimanu Kumar \\
% Carnegie Mellon University\\
% \texttt{abhimank@cs.cmu.edu}\\
% \And
% Chong Wang \\
% Carnegie Mellon University\\
% \texttt{chongw@cs.cmu.edu}\\
% \And
% Carolyn P. Rose \\
% Carnegie Mellon University\\
% \texttt{cprose@cs.cmu.edu}\\
% }

\newcommand{\fix}{\marginpar{FIX}}
\newcommand{\new}{\marginpar{NEW}}
\newcommand{\comment}[1]{{\color{red}{#1}}}

%\nipsfinalcopy

\begin{document}
\maketitle
\begin{abstract}

Thread-based online discussion forums contain rich information of user 
interactions and can potentially be used as important tools to improve 
inter-user communications. However, this information is usually encapsulated 
in the large amount of threads due to the user-specific replying structures 
and associated posts. To unravel this, we develop a probabilistic approach 
to accurately model user interactions in thread-based online forums. Our 
model integrates the merits from mixed-membership stochastic block models 
(MMSB) and probabilistic topic models. Our model enforces a one-to-one 
mapping from the community to the topic which allows easy interpretations 
of different communities using the textual information from posts.

To deal with large-scale datasets from online forums, we develop a scalable 
algorithm based on stochastic variational inference.  We evaluate our model 
on two large-scale datasets, Cancer (30K users and 200K threads) and 
StackOverFlow (xx users and xx threads). Quantitatively, we show our 
model does better than MMSB in predicting user replies. On another task 
of user survival prediction (Would the users post again?), our model 
outperforms the results from the published work [x]. In addition, we 
demonstrate that our model can provide useful explanations of user 
interactions in different communities using the topics discovered from posts.







\end{abstract}

\section{Introduction}
\input{intro}

\section{Related Work}
\input{relatedWork}

% \section{Graphical Model \& Generative Story}
\section{Approach}
\input{approach}

\section{Datasets}
\input{dataset}
% 
% \section{Our Method \& Tasks Finished}
% \input{approach&tasks}
% 
\section{Experimental Setup and Evaluation}
\input{experiments}

\section{Results}
\input{results}

\section{Conclusion \& Future Work}
\input{conclusion}

%o\section{Finished Task Split-up}

%\input{appendix}

%\input{06Eval01}
%\input{06Eval02}
\bibliography{mybib}
\bibliographystyle{plain}
\end{document}
