There have been a flood of online forums in recent decade and consequently sohave been the focus of academic research and industry on online social networks. Analysing online social networks and user forums have been approached usingvarious perspective such as graph/network ~\cite{Shi:2000:NCI:351581.351611,Shi00learningsegmentation} , probabilistic graphical model~\cite{ Airoldi:2008:MMS:1390681.1442798}, combined network \& text miningbased~\cite{Ho:2012:DHT:2187836.2187936,Nallapati:2008:JLT:1401890.1401957}based approaches.But very few of these have taken into account the structural framework in whichthe conversation in online forums happen. This is important to correctly model theinteraction as well as the contents posted by the users during theirconversation with the user community. E.g. in an onlne forum there are topic-threads and userspost their responses on this thread after possibly reading through the responsesof other users in this thread. And the users possibly posts multiple times onthe thread in the form of replies to other posts in the thread. For analysingsuch a user interaction it becomes imperative that the structure of theconversation must also be taken into account  besides taking into account the user interactionnetwork and the text posted. This enables us to gaindeeper insights into user behavior in the online community that was not possibleearlier. Very few research works have tried to bring the forum structure in theanalysis of online communities. This is what set our work apart from the past works, ourapproach here besides bringing network modeling and text mining together adds inthe forum structure in the model to provide a more robust analysis ofthe user interactions. The model also incorporates strength of interactionamong the users by incorporating interaction counts as compared to MMSB modelwhich just looks presence or absence of link~\cite{Airoldi:2008:MMS:1390681.1442798}. In the process we discover interesting online communities and social phenomena.The current work also focuses on analysing large scale user interactions in bigonline social forums. We provide a stochastic variationalapproximation~\cite{Hoffman:2013:SVI} based estimation technique that isscalable to big forums with thousands of users.% ~\comment{Also write about stochastic approximation if given we have time and we% can get it working}. 