We perform user-user link prediction tasks as well as user survival predicitionin forums besides reporting perplexity and log-likelihood convergence onheld-out test set. We also analyse and the user-communtiy vectors $\Pi$ asdefined in section~\ref{sec:approach} to show-case interesting insighst that thenewly discovered user-communities provide. \subsection{Link prediction}We hold out some users randomly in the dataset and predict theirlikelihood of interaction with other users based solely on the content of theirposts in the forum and the parameters of the model learnt in the training phase. We take the top K (1, 5 and 10) users that the model predicts for every held-outuser and report the overall precision and recall in the top-K set. This willhave to be done for a specific snapshot of the forum because not many users willhave a overlapping posting history accross their whole stay on the forum.\subsection{Cancer forum user survival prediction}Users in cancer forum posts different messages at different phases of theorcancer. It has been seen that in while users are certain cancer phase they tendto post more often and regularly. The intuition behind this prediction task isto exploit this pattern. We use the variational parameter of the$\bar{Z_{p\rightarrow}}$ to get the topic composition of a users posts in theforum at one particular snapshot of time e.g. every month or every two months.We combine the features shown to be useful for such an analysis by Wen etal.~\cite{Wen:2013:Carolyn} with the variational parameters to predict whetherthe user will post in the coming period of time e.g. within the next month ortwo months.