Online forums are a microcosm of communities where users' presentationcharacteristics vary across different parts of the forum. Users participate in adiscussion or group activity by posting on a related thread. And during hisstay in a forum, a user participates in many different discussions and posts on multiplethreads. The thread level presentation characteristics of a user are differentthan the global presentation chracteristics. A participating user gears hisresponses to suit specific discussions on different threads. These thread basedinteractions give rise to active sub-networks, within the global network of users,that characterize the dynamics of interaction. Overlaying differential changesin user interaction characteristics across these sub-networks providesinsights into users' macroscopic (forum-wide) as well as microscopic (threadspecific) participation behavior. Analysing online social networks and user forums have been approached usingvarious perspective such as graph/network ~\cite{Shi:2000:NCI:351581.351611,Shi00learningsegmentation} , probabilistic graphical model~\cite{ Airoldi:2008:MMS:1390681.1442798}, combined network \& text miningbased~\cite{Ho:2012:DHT:2187836.2187936,Nallapati:2008:JLT:1401890.1401957}based approaches. But none of the approches above in social networks have takeninto account the dynamics of sub-networks and the related thread-based structural framework inwhich the discussions in online forums happen. Whereas active-subnetwrok modelling hasbeen very useful to the research in computational biology in recent years whereit's been used to model sub-network of geneinteractions~\cite{journals/ploscb/DeshpandeSVHM10,Lichtenstein:Charleston},very few approaches using active-subnetwork have been proposed to model onlineforum user interactions. Taking into account subnetwork interactiondynamics is important to correctly model the user particiaption behavior. E.g.in an onlne forum there are topic-threads and users post their responses onthese threads after possibly reading through the responses of other users inthese threads. The users possibly post multiple times on the thread in the formof replies to other posts in the thread. For analysing such a user interaction itbecomes imperative that the structure of the conversation must also be takeninto account  besides taking into account the user interaction network and thetext posted. This enables us to gain deeper insights into user behavior in theonline community that was not possible earlier. One of the main challenges of this work has been the ability to deal withsocial network data on a large (millions of users and threads) scale. Asocial network spanning around millions of users and threads would be an idealcase to demonstrate effectiveness of active-subnetwprk modelling. To thispurpose we designed a model based on Stochastic variational The model also incorporates strength of interactionamong the users by incorporating interaction counts as compared to MMSB modelwhich just looks presence or absence of link~\cite{Airoldi:2008:MMS:1390681.1442798}. In the process we discover interesting online communities and social phenomena.The current work also focuses on analysing large scale user interactions in bigonline social forums. We provide a stochastic variationalapproximation~\cite{Hoffman:2013:SVI} based estimation technique that isscalable to big forums with thousands of users.% ~\comment{Also write about stochastic approximation if given we have time and we% can get it working}. 